Legion: Expressing Locality and Independence with Logical Regions

### 2012-08-09 doc/sc2012/conclusion.tex
Minor edits

We have presented Legion, a programming model for expressing
the abstract locality and independence properties of program
data by using logical regions.  The Legion programming model enables 
a distributed Software-Out-of-Order Processor (SOOP) scheduling 
algorithm.  The SOOP algorithm leverages the locality and independence properties
captured by logical regions to efficiently execute programs.  We also
described a novel mapping interface that guides the SOOP execution
and allows tuning of program performance independent of correctness.
We demonstrated that our SOOP runtime implementation
of Legion was faster than existing implementations of
three benchmarks and that it was able to scale on distributed, heterogeneous
machines.

>>>>

We have presented Legion, a programming model for expressing
the abstract locality and independence properties of program
data by using logical regions.  The Legion programming model enables 
a distributed Software-Out-of-Order Processor (SOOP) scheduling 
algorithm.  The SOOP algorithm leverages the locality and independence properties
captured by logical regions to efficiently execute programs.  We also
described a novel mapping interface that guides the SOOP execution
and allows tuning of program performance independent of correctness.
We demonstrated that for three benchmarks our SOOP runtime 
enabled Legion implementations that were faster than existing codes
and that the SOOP was able to scale on distributed, heterogenous machines.
